%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.5in,top=0.6in,right=0.5in,bottom=0.6in]{geometry} % Document margins

\name{Alexander Safatli} % Your name
\address{Herring Cove \\ Halifax, NS, Canada B3R2N8} % Your address
\address{(902) 222-2084 \\ alex@safatli.com} % Your phone number and email
\address{\textsc{GitHub} AlexSafatli \\ \textsc{LinkedIn} asafatli \\ \texttt{alex.safatli.com}} % Github, Linkedin, web

\begin{document}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Liberated Networks}{December 2018 -- September 2019 (part-time 2020 -- 2021)}{Intermediate Software Developer}{Bedford, NS}
\item Maintenance of several ASP.NET applications contracted out to national ISPs. \textit{C\# and JavaScript}.
\item Exploration of machine learning techniques when applied to resumes and job matching. \textit{Python}.
\item Partial ownership of a Kanban-like stack. \textit{Java Spring and Angular 7}.
\end{rSubsection}

\begin{rSubsection}{BeyondTrust}{January 2017 -- January 2018}{Software Engineer}{Halifax, NS}
\item Maintained full stack cybersecurity software deployment panel packaged with software marketed to Fortune 100 companies. \textit{Go, Angular, TypeScript}.
\item Monitored services and managed tooling and devops for the team. \textit{Jenkins, Docker}.  
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Amazon}{December 2015 -- January 2017}{Software Development Engineer I}{Seattle, WA}
\item Touched, maintained, and real-time diagnosed many components of the website and microservice architecture underlying it (was on team focused on payment methods). \textit{Java, C++, Perl, Ruby, Go, and Python}.
\item Served on-call on a regular monthly basis to monitor and manage large demand web services and platforms. Dealt with high-severity issues a number of times that impacted millions of customers.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{watzan, LLC}{June 2015 -- December 2015}{Software Developer}{Seattle, WA}
\item Touched, maintained, and real-time diagnosed many components of the website and microservice architecture underlying it (was on team focused on payment methods). \textit{Java, C++, Perl, Ruby, Go, and Python}.
\item Served on-call on a regular monthly basis to monitor and manage large demand web services and platforms. Dealt with high-severity issues a number of times that impacted millions of customers.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Dalhousie University, Canada} \hfill {June 2015, September 2019-2024} \\
PhD in Computer Science (\textit{incomplete}, fulfilled all coursework, partial thesis/seminar requirements) --- 2019-2022 \\
M.S.E. in Computer Science (GPA 4.3) --- September 2015 \\
B.S.E. in Computer Science (GPA 4.0, in-major) --- May 2014 \smallskip \\
\textit{Coursework}. Adv. Algorithms, Algorithms, Data Structures, NLP, Visual Analytics, OS, DBs, Software Engineering, \\
Principles of Prog. Languages, Architecture, Cryptography, Discrete Math \textit{et al.} \smallskip \\
\textit{Extracurricular}. Secretary of CS Graduate Society, CS Society

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{1ex}} l }
Languages & \textit{Experienced}. Go, C, Python, C++, Java/Scala, C\#. \textit{Familiar}. Typescript, Dart, Ruby, Lua, Prolog, Swift. \\
Frameworks & Angular, ASP.NET, Ruby on Rails, Flask, Vue, React, Flutter, Django, Mason, Tensorflow \\ 
Databases & MySQL, PostgreSQL, Microsoft SQL, Mongo, Dynamo, Redis \\
Tools & Git, SVN, Mercurial, Docker, \LaTeX, Unix (ricing, GNU, etc.), AWS, \texttt{bash}, \texttt{zsh}, \texttt{vim}, \texttt{emacs} \\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Select Projects, Papers \& Awards}

\begin{description}
\item [\textit{Pylogeny} (2016)] Framework for combinatorics in phylogeny. Peer-reviewed and published in \textit{PeerJ}. \textit{Python}.
\item [ABeRMuSA (2016)] CLI that performs multiple 3D protein structure alignment. \textit{Python}.
\item [Undergraduate Student Research Award (NSERC) (2009, 2012, 2013)] Summer research internship placements.
\end{description}

\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}

