\cvsection{Work Experience}

\begin{cventries}

  \cventry
    {Intermediate Software Developer} % Job title
    {Liberated Networks} % Organization
    {Halifax, Canada} % Location
    {Dec. 2018 - Sep. 2021} % Date(s)
    {
      \begin{cvitems}
        \item {Maintained and owned many C\# ASP.NET applications contracted out to major national ISPs for use in their daily operations that served as a major component in their supply chain.}
        \item {Explored a number of machine learning techniques and took point for an R\&D area in resume and job matching that was a sought after new avenue of business for the company.}
        \item {Took partial ownership of a Kanban-like Angular stack used for work and resource procurement in Atlantic Canada that was used by hundreds of thousands of employees.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {BeyondTrust} % Organization
    {Halifax, Canada} % Location
    {Jan. 2017 - Jan. 2018} % Date(s)
    {
      \begin{cvitems}
        \item {Was one of three members tasked with and performed a large part of the software architecture, and later maintenance, of a full stack Angular/Go cybersecurity software deployment suite packaged with other key products from the company marketed to Fortune 100 companies. This software suite was highly praised and is the entry point for product users to install these products.}
        \item {Monitored services and managed tooling and devops for the team using tools like Jenkins, Docker, and Kubnernetes.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer Engineer I} % Job title
    {Amazon} % Organization
    {Seattle, USA} % Location
    {Dec. 2015 - Jan. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Touched, maintained, and real-time diagonsed many components of the website and microservice architecture underlying the Amazon web platform.}
        \item {Was on the payment methods team and took the lead of both the cart convergence project that combined a dedicated gift card cart with the main cart people know when using the site. Also took lead in a project enabling cross-border redemption of gift cards bought in one country so they can be redeemed in another, writing regression tests, metrics, and code end-to-end.}
        \item {Served on-call on a regular monthly basis to monitor and manage large demand payment method services dealing with high severity issues in a timely manner that impacted millions of customers.}
      \end{cvitems}
    }

\end{cventries}
